Searching for flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-03-07 src/tex/ms.tex
[showyourwork] overleaf sync

The bulk of the systems in our sample are neither expected to show high power of magnetic star-planet interaction, nor do they show any deviation from intrinsic stellar flaring that could be indicative of flaring star-planet interaction. In the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring star-planet interaction with increasing expected power $P$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522~(Sections \ref{sec:results:individualstars:aumic}-\ref{sec:results:individualstars:hip67522}). Then we consider those systems where high power was expected in all scenarios, but not measured, i.e., TAP 26 and KOI-12~(Sections \ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}).
\subsubsection{Excluded targets}
\label{sec:results:individualstars:excluded}

@@

\subsubsection{AU Mic}
\label{sec:results:individualstars:aumic}

@@

\subsubsection{K2-25}
\label{sec:results:individualstars:k225}
\subsubsection{TOI-540}
\label{sec:results:individualstars:toi540}

\subsubsection{HIP 67522}
\label{sec:results:individualstars:hip67522}
HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest signs of flaring SPI, albeit with only 6 flares in the sample. These flares are distributed across two Sectors in TESS. In Sector 11, two flares occur at orbital phases $\sim 0.6$ and $\sim 0.8$. Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, up to a few hours after transit.

>>>>

The bulk of the systems in our sample are neither expected to show high power of magnetic star-planet interaction, nor do they show any deviation from intrinsic stellar flaring that could be indicative of flaring star-planet interaction. In the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring star-planet interaction with increasing expected power $P$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522~(Sections \ref{sec:results:individualstars:aumic} and \ref{sec:results:individualstars:hip67522}). Then we consider those systems where high power was expected in all scenarios, but not measured, i.e., TAP 26 and KOI-12~(Sections \ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}).
\subsubsection{Excluded targets}
\label{sec:results:individualstars:excluded}

@@

\subsubsection{AU Mic, K2-25, and TOI-540}
\label{sec:results:individualstars:aumic}

@@

K2-25 is a multiplanet system around a fast rotating ($<2\,$d) mid-M dwarf in the Hyades open cluster, that is, 600-800 Myr old~\citep{stefansson2020habitable}. Both the expected power of interaction, and the measured deviation, are remarkably similar to the AU Mic system. Moreover, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits~\citep{rockcliffe2021lya}. This might at least in part be due to the stellar wind conditions around K2-25 b. Further investigation of magnetic star-planet interactions, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius.

In Figure~\ref{fig:adtest_bp}, TOI-540 clusters with K2-25 and AU Mic -- a fast rotating M dwarf with its innermost planet in a $1.24\,$d orbit~\citep{ment2021toi}. Compared to the other two systems, its innermost planet is not a Neptune, but a rocky planet slightly smaller than Earth~\citep{ment2021toi}. It is a relatively smaller obstacle in the host's magnetic field, yet the interaction is expected to be of a similar magnitude due to the strongest inferred magnetic field and closest orbit among the three systems.

In the scenario wherein the stretch-and-break mechanism drives the interaction, the three system cluster together most distinctly. In this scenario, they 
\subsubsection{HIP 67522}
\label{sec:results:individualstars:hip67522}
HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest signs of flaring SPI, albeit with only 6 flares in the sample. These flares are distributed across two Sectors in TESS. In Sector 11, two flares occur at orbital phases $\sim 0.6$ and $\sim 0.8$. Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, up to a few hours after transit.
